\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects for Robust Grasp Planning Using a Multi-Armed Bandit Model with Correlated Rewards \vspace{-2ex} \versionline{11}

### 2015-09-16 ICRA2016/bandits_docs/includes/introduction.tex
Adding tex for submitted version of paper

\begin{figure}[t!]
\centering
\includegraphics[scale=0.45]{figures/illustrations/spray_bottle_avg_reward_w_neighbors.eps}
\caption{Average normalized grasp quality versus iteration over 25 trials for the Dex-Net 10 algorithm with 1,000 and 10,000 prior 3D objects (bottom) and illustrations of five nearest neighbors in Dex-Net (top) for a spray bottle. We measure quality by the probability of force closure of the best grasp predicted by the algorithm on each iteration and compare with Thompson sampling without priors and uniform allocation. (Top) The spray bottle has no similar neighbors with 1,000 objects, but two other spray bottles are found by the MV-CNN in the 10,000 object set. (Bottom) As a result, the Dex-Net 1.0 algorithm does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimal grasp with 10,000 prior objects.}
\figlabel{avg-reward-spray}
\vspace*{-20pt}
\end{figure}
The primary contribution of this paper is an algorithm based on a Multi-Armed Bandit (MAB) model with correlated rewards to speed up robust planning by learning from a large dataset of prior grasps and 3D object models.
The algorithm is based on Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a belief distribution on the quality of each grasp from prior data.

To study scaling effects we developed Dex-Net 1.0, a growing dataset that currently includes over 10,000 3D object models selected to reflect objects that could be encountered in warehousing or the home such as containers, tools, tableware, and toys.
Dex-Net also contains approximately 2.5 million parallel-jaw grasps, and each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
To the best of our knowledge, this is the largest object dataset used for grasping research to-date.
We also incorporate Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects.

We implement the algorithm on Google Compute Engine and store Dex-Net 1.0 on Google Cloud Storage, with a system that can run up to 1,500 instances at once.
Experiments suggest that using 10,000 prior object models from Dex-Net can reduce the average number of samples needed to plan robust parallel-jaw grasps by up to 2$\times$.
%\TODO{Update with final results}

>>>>

\begin{figure}[t!]
\centering
\includegraphics[scale=0.45]{figures/illustrations/spray_bottle_avg_reward_w_neighbors.eps}
\caption{Normalized grasp quality versus iteration averaged over 25 trials for the Dex-Net 1.0 algorithm with 1,000 and 10,000 prior 3D objects (bottom) and illustrations of five nearest neighbors in Dex-Net (top) for a spray bottle. We measure quality by the probability of force closure of the best grasp predicted by the algorithm on each iteration and compare with Thompson sampling without priors and uniform allocation. (Top) The spray bottle has no similar neighbors with 1,000 objects, but two other spray bottles are found by the MV-CNN in the 10,000 object set. (Bottom) As a result, the Dex-Net 1.0 algorithm does not outperform Thompson sampling for 1,000 objects, but quickly converges to the optimal grasp with 10,000 prior objects.}
\figlabel{avg-reward-spray}
\vspace*{-20pt}
\end{figure}
The primary contribution of this paper is an algorithm based on a Multi-Armed Bandit (MAB) model with correlated rewards to speed up robust planning by learning from a large dataset of prior grasps and 3D object models.
The algorithm is based on Continuous Correlated Beta Processes (CCBPs)~\cite{goetschalckx2011continuous, montesano2012active}, an efficient model for predicting a belief distribution on the quality of each grasp from prior data.

To study scaling effects, we developed Dex-Net 1.0, a growing dataset that currently includes over 10,000 unique 3D object models selected to reflect objects that could be encountered in warehousing or the home such as containers, tools, tableware, and toys.
Dex-Net also contains approximately 2.5 million parallel-jaw grasps, as each object is labelled with up to 250 grasps and an estimate of the probability of force closure for each under uncertainty in object pose, gripper pose, and friction coefficient.
To the best of our knowledge, this is the largest object dataset used for grasping research to-date.
We also incorporate Multi-View Convolutional Neural Networks (MV-CNNs)~\cite{su2015multi}, a state-of-the-art method for 3D shape classification, to efficiently retrieve similar 3D objects.

We implement the algorithm on Google Compute Engine and store Dex-Net 1.0 on Google Cloud Storage, with a system that can run up to 1,500 instances at once.
Experiments suggest that using 10,000 prior object models from Dex-Net reduces the number of samples needed to plan robust parallel-jaw grasps by up to 2$\times$ on average over 45 objects.
%\TODO{Update with final results}

### 2015-09-16 ICRA2016/bandits_docs/includes/problem_statement.tex
Adding tex for submitted version of paper

We consider the robust grasp planning problem for a given 3D object model and parallel-jaw grippers using probability force closure ($P_F$)  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
We assume the object shape is provided as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp}, which is zero on the object surface, positive outside the object, and negative within. 
The object is specified in units of meters with given center of mass $\bz \in \mathbb{R}^3$.
We assume soft-finger contacts with a Coulomb friction model~\cite{zheng2005} and that the gripper jaws are opened to their maximal width $w \in\bR$ before closing on the object.
%and known uncertainty in object pose, gripper pose relative to the object, and friction coefficient, described in detail in \seclabel{uncertainty} below.

@@

\subsection{Sources of Uncertainty}
\seclabel{uncertainty}
We assume Gaussian distributions on object pose, gripper pose, and friction coefficient to model errors in registration, robot calibration, or classification material properties, respectively. 
We denote by $\mN(\mu,\Sigma)$ a Gaussian distribution with mean $\mu$ and variance $\Sigma$.
Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
We define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$.
Let $\nu \sim \mN\left(\mu_{\nu}, \Sigma_{\nu}\right)$ denote a Gaussian distribution on gripper pose with mean $\mu_{\nu} \in \mG$.
Let $\gamma \sim \mN\left(\mu_{\gamma}, \Sigma_{\gamma} \right)$ denote a Gaussian distribution on friction coefficient with mean $\mu_{\gamma} \in \mathbb{R}$.
We denote by $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$ samples of the random variables.

@@

Let $F \in \{0, 1\}$ denote the occurrence of force closure.
Then for a grasp $\bg$ on object $\mO$, $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$.
To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\hat{\xi}$, gripper pose $\hat{\nu}$, and friction coefficient $\hat{\gamma}$, we first compute the set of possible contact wrenches $\mW$.
Then $F = 1$ if $\mathbf{0} \in Conv(\mW)$, where $Conv(\cdot)$ denotes the convex hull~\cite{weisz2012pose}.

\subsection{Objective}
We are interested in finding a grasp $\bg^*$ that maximizes $P_F(\bg)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}.
As the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits (MAB) ~\cite{laskey2015bandits}.
In this work, we extend the 2D MAB model of~\cite{laskey2015bandits} to leverage similarities between grasps and prior 3D objects in Dex-Net to reduce the number of samples~\cite{hoffman2013exploiting, pandey2007multi}.

>>>>

We consider the robust grasp planning problem for a given 3D object model and parallel-jaw grippers using probability of force closure ($P_F$)  under uncertainty in object pose, gripper pose, and friction coefficient as a grasp quality metric.
We assume the nominal object shape is given as a signed distance function (SDF) $f: \mathbb{R}^3 \rightarrow \mathbb{R}$~\cite{mahler2015gp}, which is zero on the object surface, positive outside the object, and negative within. 
The object is specified in units of meters with given center of mass $\bz \in \mathbb{R}^3$.
We assume soft-finger contacts with a Coulomb friction model~\cite{zheng2005} and that the gripper jaws are opened to their maximal width $w \in\bR$ before closing on the object.
%and known uncertainty in object pose, gripper pose relative to the object, and friction coefficient, described in detail in \seclabel{uncertainty} below.

@@

\subsection{Sources of Uncertainty}
\seclabel{uncertainty}
We assume Gaussian distributions on object pose, gripper pose, and friction coefficient to model errors in registration, robot calibration, or classification material properties, respectively. 
We denote by $\mN(\mu,\Sigma)$ a Gaussian distribution with mean $\mu$ and variance $\Sigma$.
Let $\upsilon \sim \mN\left(\mathbf{0}, \Sigma_{\upsilon}\right)$ denote a zero-mean Gaussian on $\bR^6$ and $\mu_{\xi} \in SE(3)$ be a mean object pose.
We define the object pose random variable $\xi = \exp\left( \upsilon^{\wedge} \right) \mu_{\xi}$, where the $\wedge$ operator maps from $\bR^6$ to the Lie algebra $\mathfrak{se}(3)$~\cite{barfoot2014associating}.
Let $\nu \sim \mN\left(\mathbf{0}, \Sigma_{\nu}\right)$ denote zero-mean Gaussian gripper pose uncertainty with mean $\mu_{\nu} \in \mG$.
Let $\gamma \sim \mN\left(\mu_{\gamma}, \Sigma_{\gamma} \right)$ denote a Gaussian distribution on friction coefficient with mean $\mu_{\gamma} \in \mathbb{R}$.
We denote by $\hat{\xi}, \hat{\nu},$ and $\hat{\gamma}$ samples of the random variables.

@@

Let $F \in \{0, 1\}$ denote the occurrence of force closure.
For a grasp $\bg$ on object $\mO$, $P_F(\bg, \mO) = \mathbb{P}\left(F = 1 \mid \bg, \mO, \xi, \nu, \gamma \right)$.
To compute force closure for a grasp $\bg \in \mG$ on object $\mO \in \mH$ given samples of object pose $\hat{\xi}$, gripper pose $\hat{\nu}$, and friction coefficient $\hat{\gamma}$, we first compute the set of possible contact wrenches $\mW$.
Then $F = 1$ if $\mathbf{0} \in Conv(\mW)$, where $Conv(\cdot)$ denotes the convex hull~\cite{weisz2012pose}.

\subsection{Objective}
We are interested in finding a grasp $\bg^*$ that maximizes $P_F(\bg)$~\cite{kim2012physically, laskey2015bandits, mahler2015gp, weisz2012pose} over a budgeted maximum number of samples $T$.
To perform this as quickly as possible we maximize over the sum of the $P_F$ for all sampled grasps~\cite{laskey2015bandits, srinivas10gaussian}.
Since the maximization over the continuous space $\mG$ is computationally expensive, past work has solved this objective by evaluating a discrete set of $K$ candidate grasps $\Gamma = \left\{ \bg_1, ..., \bg_K \right\}$ with Monte-Carlo integration~\cite{kehoe2012toward, weisz2012pose} or Multi-Armed Bandits (MAB) ~\cite{laskey2015bandits}.
In this work, we extend the 2D MAB model of~\cite{laskey2015bandits} to leverage similarities between grasps and prior 3D objects in Dex-Net to reduce the number of samples~\cite{hoffman2013exploiting, pandey2007multi}.

### 2015-09-16 ICRA2016/bandits_docs/includes/related_work.tex
Adding tex for submitted version of paper

Grasp planning considers the problem of finding grasps for a given object that achieve force closure or optimize a related quality metric~\cite{pokorny2013c}.
Usually it is assumed that the object is known exactly and that contacts are placed exactly, and mechanical wrench space analysis is applied.
Robust grasp planning considers the same problem in the presence of bounded perturbations in properties such as object shape, pose, or mechanical properties such as friction, which are inevitable due to imprecision in perception and control.
One way to treat perturbations is statistical sampling.
Since sampling in high dimensions can be computationally demanding, recent work has explored how a robust grasps computed from one object can guide the search for robust grasps on similar objects~\cite{bohg2014data}, for example by warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia, goldfeder2011data} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated using the GraspIt! stochastic sampling-based grasp planner.
%This led to research on methods for transferring grasps from objects in databases, such as warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.

Recent research has studied labelling grasps in a database with metrics that are robust to imprecision in perception and control using probability of force closure ($P_F$)~\cite{weisz2012pose} or expected Ferrari-Canny quality~\cite{kim2012physically}.
Experiments by Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} suggest that the robust metrics are better correlated with success on a physical robot than deterministic WS metrics.
Brook et al.~\cite{brook2011collaborative} planned robust grasps for a database of 892 point clouds and developed a model to predict grasp success on a physical robot based on correlations with grasps in the database.   
Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by $P_F$ on 100 objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine, and achieved 80\% success in grasping objects on a table.

Another line of research has focused on synthesizing grasps using statistical models~\cite{bohg2014data} learned from a database of images~\cite{lenz2015deep} or point clouds~\cite{detry2013learning, herzog2014learning, zhang2011graspable} of objects annotated with grasps from human demonstrators~\cite{herzog2014learning, lenz2015deep} or physical execution~\cite{herzog2014learning}.
Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface.
We estimate $P_F$ using similar objects and grasps using a variant of the Multi-Armed Bandit (MAB) model for sequential decision-making.

Our work is also closely related to research on actively sampling grasps to build a statistical model of grasp quality from fewer examples~\cite{detry2011learning, kroemer2010combining, salganicoff1996active}.
%Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discarding grasps known to have poor quality.
%Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
%Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
%Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
%Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, and measured correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
Oberlin and Tellex~\cite{oberlin2015autonomously} developed a budgeted MAB algorithm for planning 3 DOF crane grasps a using priors from the responses of hand-designed depth image filters, but did not study the effects of orders of magnitude of prior data on convergence.
Recently, Laskey et al.~\cite{laskey2015bandits} used MAB algorithms to reduce the number of samples needed to identify grasps with high $P_F$ under uncertainty in object shape, pose, and friction in 2D.
%MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
In this work we extend the model of~\cite{laskey2015bandits} to 3D and study the scaling effects of using prior data from Dex-Net on planning grasps with high $P_F$.

% DEEP LEARNING
To use the prior information contained in Dex-Net, we also draw on research on 3D model similarity.
One line of research has focused on shape geometry, such as characteristics of harmonic functions on the shape~\cite{bronstein2011shape}, or CNNs trained on a voxel representation of shape~\cite{maturana2015voxnet, wu20153d}.
Onother line of research relies on the description of rendered views of a 3D model~\cite{chen2003visual, goldfeder2011data}.
One of the key difficulty of these methods is to aggregate or compare views from different objects, which may be oriented inconsistently.
The recent work of Su et al.~\cite{su2015multi} addresses this issue by using CNN trained for ImageNet classification as descriptors for the different views and aggregating them with a second CNN that learns the invariance to orientation.
Using this method, the authors improve state-of-the-art classification accuracy on ModelNet40 by 10\%.
We use a max-pooling to aggregate views, similar to the average pooling proposed in~\cite{aubry2015understanding}.
% proposed a simpler average pooling of the features from different views.

>>>>

Grasp planning considers the problem of finding grasps for a given object that achieve force closure or optimize a related quality metric~\cite{pokorny2013c}.
Usually it is assumed that the object is known exactly and that contacts are placed exactly, and mechanical wrench space analysis is applied.
Robust grasp planning considers the same problem in the presence of bounded perturbations in properties such as object shape, pose, or mechanical properties such as friction, which are inevitable due to imprecision in perception and control.
One way to treat perturbations is statistical sampling.
Since sampling in high dimensions can be computationally demanding, recent work has explored how a robust grasp computed from one object can guide the search for robust grasps on similar objects~\cite{bohg2014data}, for example by warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.
To study grasp planning at scale, Goldfeder et al.~\cite{goldfeder2009columbia, goldfeder2011data} developed the Columbia grasp database, a dataset of 1,814 distinct models and over 200,000 force closure grasps generated using the GraspIt! stochastic sampling-based grasp planner.
%This led to research on methods for transferring grasps from objects in databases, such as warping contacts~\cite{stouraitis2015functional} or interpolating grasps and shapes over a Grasp Moduli Space~\cite{pokorny2013grasp}.

Recent research has studied labelling grasps in a database with metrics that are robust to imprecision in perception and control using probability of force closure ($P_F$)~\cite{weisz2012pose} or expected Ferrari-Canny quality~\cite{kim2012physically}.
Experiments by Weisz et al.~\cite{weisz2012pose} and Kim et al.~\cite{kim2012physically} suggest that the robust metrics are better correlated with success on a physical robot than deterministic wrench space metrics.
Brook et al.~\cite{brook2011collaborative} planned robust grasps for a database of 892 point clouds and developed a model to predict grasp success on a physical robot based on correlations with grasps in the database.   
Kehoe et al.~\cite{kehoe2013cloud} created a Cloud-based system to transfer grasps evaluated by $P_F$ on 100 objects in a database to a physical robot by indexing the objects with the Google Goggles object recognition engine, and achieved 80\% success in grasping objects on a table.

Another line of research has focused on synthesizing grasps using statistical models~\cite{bohg2014data} learned from a database of images~\cite{lenz2015deep} or point clouds~\cite{detry2013learning, herzog2014learning, zhang2011graspable} of objects annotated with grasps from human demonstrators~\cite{herzog2014learning, lenz2015deep} or physical execution~\cite{herzog2014learning}.
Kappler et al.~\cite{kappler2015leveraging} created a database of over 700 object instances, each labelled with 500 Barrett hand grasps and their associated quality from human annotations and the results of simulations with the ODE physics engine.
The authors trained a deep neural network to predict grasp quality from heightmaps of the local object surface.
We estimate $P_F$ using similar objects and grasps using a variant of the Multi-Armed Bandit (MAB) model for sequential decision-making.

Our work is also closely related to research on actively sampling grasps to build a statistical model of grasp quality from fewer examples~\cite{detry2011learning, kroemer2010combining, salganicoff1996active}.
%Kehoe et al.~\cite{kehoe2012estimating} proposed iterative pruning, an algorithm for evaluating the probability of force closure for a set of candidate grasps while discarding grasps known to have poor quality.
%Detry et al.~\cite{detry2011learning} estimated a full continuous density function over grasp poses using kernel density estimation and adaptively acquired samples by pruning unsuccessful grasps.
%Kroemer et al.~\cite{kroemer2010combining} developed a reinforcement learning approach to grasp selection based on seeding hypotheses via imitation learning and Gaussian process upper-confidence bounds for active grasp acquisition.
%Boularias et al.~\cite{boularias2014efficient, boularias2015learning} used a Gaussian process Bayesian Optimization model for selecting grasps on cluttered piles of rocks.
%Salaganicoff et al.~\cite{salganicoff1996active} used active learning to decide the next grasp to execute on a physical robot while learning a predicitve model of empirical success from range sensors.
Montesano and Lopes~\cite{montesano2012active} used Continuous Correlated Beta Processes~\cite{goetschalckx2011continuous} to actively acquire grasp executions on a physical robot, and measured correlations from the responses to a bank of image filters designed to detect grasp affordances such as edges.
Oberlin and Tellex~\cite{oberlin2015autonomously} developed a budgeted MAB algorithm for planning 3 DOF crane grasps using priors from the responses of hand-designed depth image filters, but did not study the effects of orders of magnitude of prior data on convergence.
Recently, Laskey et al.~\cite{laskey2015bandits} used MAB algorithms to reduce the number of samples needed to identify grasps with high $P_F$ under uncertainty in object shape, pose, and friction in 2D.
%MAB algorithms trade off gaining information about grasps that have been sampled fewer times with exploiting the grasp with the highest estimated quality given the past samples.
In this work we extend the model of~\cite{laskey2015bandits} to 3D and study the scaling effects of using prior data from Dex-Net on planning grasps with high $P_F$.

% DEEP LEARNING
To use the prior information contained in Dex-Net, we also draw on research on 3D model similarity.
One line of research has focused on shape geometry, such as characteristics of harmonic functions on the shape~\cite{bronstein2011shape}, or CNNs trained on a voxel representation of shape~\cite{maturana2015voxnet, wu20153d}.
Another line of research relies on the description of rendered views of a 3D model~\cite{chen2003visual, goldfeder2011data}.
One of the key difficulty of these methods is comparing views from different objects, which may be oriented inconsistently.
The recent work of Su et al.~\cite{su2015multi} addresses this issue by using CNN trained for ImageNet classification as descriptors for the different views and aggregating them with a second CNN that learns the invariance to orientation.
Using this method, the authors improve state-of-the-art classification accuracy on ModelNet40 by 10\%.
We use a max-pooling to aggregate views, similar to the average pooling proposed in~\cite{aubry2015understanding}.
% proposed a simpler average pooling of the features from different views.

### 2015-09-16 ICRA2016/bandits_docs/paper.tex
Adding tex for submitted version of paper

\section{Acknowledgments}
{\small
This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS)``People and Robots" Initiative: http://robotics.citris-uc.org.
The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, and by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab.
We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahanna Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
}

>>>>

\section{Acknowledgments}
{\small
This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS)``People and Robots" Initiative: http://robotics.citris-uc.org.
The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, and by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab.
We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahaana Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
}
